Generate Frame Measures

### 2022-04-20 data-cleaning/07-generate-frame-measures.Rmd
verified

9:15

@@

```{r}
amicus %>% head(5) 
```

@@

```{r}
sum_amicus <- amicus %>% select(case, id, forgau:sgauo) %>% 
  pivot_longer(., cols = c(forgau:sgauo), names_to = "author_type", values_to = "value") %>% 
  left_join(., amicus_frames, by = "id") %>%
  select(case, id, author_type, value, contains("freq")) %>% 
  filter(value == 1)

sum_amicus %>% head()
```
Then, sum up values by case, amicus type

>>>>

@@

@@

```{r}
sum_amicus <- amicus %>% select(case, id, forgau:sgauo) %>% 
  pivot_longer(., cols = c(forgau:sgauo), names_to = "author_type", values_to = "value") %>% 
  filter(value == 1) %>% 
  left_join(., amicus_frames, by = "id") %>%
  select(case, id, author_type, value, contains("freq"))

sum_amicus %>% head()
```
```{r}
sum_amicus %>% filter(case == "Anders v Floyd" | case == "Ayotte v. PP")
```

Then, sum up values by case, amicus type
